Self Regulation Ontology Retest Analyses

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
updates
fixing figures for paper

```{r, message=FALSE, warning=FALSE, include=FALSE}
source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Helper_Functions.R')
theme_set(theme_bw())

@@

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Helper_Functions.R')

theme_set(theme_bw())

@@

```{r}
rel_comp %>% 
  group_by(task) %>%
  summarise(mean_rr = mean(retest_reliability))
```
